\documentclass[twoside,thesis,twoadvisorsreader]{npsreport}

\usepackage{doc,lipsum} % provides \BibTex and \lipsum macros, for demos
\usepackage{acronym}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{amsmath}  %useful for multi-line equations

\usepackage{listings} %Used to post C++ code
\usepackage{xcolor}
\lstset { %
    language=C++,
    backgroundcolor=\color{black!5}, % set backgroundcolor
    basicstyle=\footnotesize,% basic font setting
}


\usepackage{graphicx}
\graphicspath{{figs/}}

\newcommand{\Lone}{$\mathcal{L}_1$ }
\newcommand{\degrees}{$^{\circ}$}

%
% For Example: you might find one of these useful:

%\usepackage{epstopdf}        % to use .eps files for figures
%\usepackage{bm}              % bold math if you need bold greek letters
%\usepackage{glossaries}      % see http:}/en.wikibooks.org/wiki/LaTeX/Glossary
%\usepackage{asymptote}       % for graphics
% The asymptote package allows for very nice graphics and figures
% Proper usage requires additional information located at:
% http://asymptote.sourceforge.net/
% See the gallery at this URL for examples

%\usepackage{placeins}        % float placement
% Provides \FloatBarrier which keeps figures/tables in the same section.
% LaTeX sometimes moves them to fill up pages.
% http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/placeins/placeins-doc.pdf

%\usepackage[numbered]{mcode} % matlab code
% The mcode package must be separately downloaded.
% http://www.mathworks.com/matlabcentral/fileexchange/8015-m-code-latex-package

%\usepackage{flafter}         % float placement
% Ensures that figures/tables do not appear in the document before
% they are referenced in the text.


\title{Engineering of Fast and Robust Adaptive Control for Fixed-Wing Unmanned Aircraft}

% Student info
\author{Ryan G. Beall}
\rank{LT, USN}
\degree{Master of Science in Systems Engineering}
\degreeabbreviation{MS}   % Should be MS, MBA or MA
\prevdegrees{B.S., United States Naval Academy, 2008} % previous degree

% Department info
\department{Department of Systems Engineering}
\thesisadvisorone{Oleg A. Yakimenko}
\thesisadvisortwo{Vladimir N. Dobrokhodov}
\secondreader{Fotis A. Papoulias}
\departmentchair{Ronald E. Giachetti}

% The date you are graduating:
\degreedate{June 2017}

% See Thesis processor's release form for approved distribution statements.
\distribution{Approved for public release. Distribution is unlimited}

% Your abstract.  New paragraphs start after an empty line.
\abstract{
Due to the incraesing demand for autonomous unmanned systems, the Department of Defense (DOD) will soon have increased difficulty in managing costs and delievery schedule.  Unmanned Aerial System (UAS) technology has advanced significantly over the past decade accelerating the use of autonomous systems both in the DOD as well as the commerical sector.  As the demand for UAS technology increases, the current Guidance Navigation and Control (GNC) algorithms will prove to poorly scale to meet the demand.  Currently, significant resources are required to certifiy flight controllers on an individual platform basis.  As different airframes are introduced to meet the expanding mission requirements, the resorces required to sustain the GNC certification demand will become a limiting factor in scalability.\newline \newline
The feasibility of replacing conventional GNC techniques for stabilizing aircraft attitude with modern adaptive control theory was conducted on Commerical off the Shelf (COTS) opensource autopilots.  COTS autopilots and open source software enabled rapid prototyping and integration of an adaptive controller with limited resources.  It was determined that the adaptive control algorithm successfully stabilized aircraft attitude with improved performance over conventional controllers.  The adaptive controller architecture was designed specifically to be aircraft non-specific to ensure the controller easily scales to minimize the resource burden of tuning and certification.  The adaptive controller tested in this research improved performance over the baseline controller and was rapidly integrated on multiple various airframes with minimal resources.
}

% Switch the below lines around, if FOUO
\securitybanner{}  
%\securitybanner{FOR OFFICIAL USE ONLY}

%
% Mandatory fields for the SF298.
%
\ReportType{Master's Thesis}
\ReportDate{[Month Year]}       % for a thesis, graduation date
\SponsoringAgency{N/A}          % really, for technical reports
\DatesCovered{MM-DD-YYYY to MM-DD-YYYY}
\ReportClassification{Unclassified}
\AbstractClassification{Unclassified}
\PageClassification{Unclassified}
%
% Optional fields for the SF298.
%
\RPTpreparedFor{}
\ContractNumber{}
\GrantNumber{}
\ProgramElementNumber{}
\TaskNumber{}
\WorkUnitNumber{}
\POReportNumber{}
\Acronyms{}
\SMReportNumber{}
\SubjectTerms{}
\ResponsiblePerson{}
\RPTelephone{}
\SignatureOne{}
\SignatureTwo{}
\SupplementaryNotes{The views expressed in this document are those of
  the author and do not reflect the official policy or position of the
  Department of Defense or the U.S. Government. %
  IRB Protocol Number: N/A. % if you need to note an IRB Protocol or N/A
}

% Optional. Prevents footnotes from being reset at each chapter
% Comment this out to have them reset with each chapter.
\makeatletter
\@removefromreset{footnote}{chapter}
\makeatother

% Optional. Adds pdf metadata and links.
% This should be right before the \begin{document}, to be the
% last package / macros defined. (Hyper-ref is fragile,
% needs to be last, and has known conflicts with other packages.)
% Comment out if you have build problems building with hyperref
\NPShyperref

%
% Your thesis begins here
%
\begin{document}

\NPScover                  	% Cover page
%\NPSsftne                  		% SF298 form
%\NPSsignature             	% Tech Report page (iii): signature page
\NPSthesistitle            	% Thesis page (iii): title page
\NPSabstractpage           	% Abstract Page
\NPSfrontmatter            	% NPS front matter follows

% This changes the chaptermark and includes the various tables
% It must be here.
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\chaptername}\ \thechapter.\ #1}{}}

%
% If you don't need one of these, comment it out.
%
\NPStableOfContents
\NPSlistOfFigures
%\NPSlistOfTables
\NPSlistOfAcronymsFromFile{acronyms}

\NPSexecsummary{
The field of adaptive control offers techniques for increasing performance and robustness in numerous settings and applications.  Adaptive control is different than traditional feedback in that it offers a mechanism for adjusting the controller's parameters to reduce plant uncertainty.  Traditional feedback control utilizes parameters, which are specified by the engineer to optimize an ideal use case, which often times requires extensive tuning and testing.  Adaptive controllers adjust their control parameters using various intelligent mechanisms designed to   increase robustness to plant variation or unanticipated disturbances.  Adaptive control has many applications in the aerospace domain to include control strategies when aerodynamic coefficients are unknown or are non-constant, actuator failure, airframe damage, etc.   This research evaluates fixed wing UAS controller performance and robustness using the \Lone adaptive control architecture. 
}

\NPSacknowledgements{
I would like to thank.....

}

% Start layout for the NPS body
\NPSbody


% CHAPTERS
\input{chapter1} 	%Introduction and History
\input{chapter2} 	%Background and Literature Review
\input{chapter3}	%L1 Adaptive Control Derivation
\input{chapter4} 	%Design of Experimental Platform
\input{chapter5} 	%Flight Testing and Performance Evaluation
\input{chapter6} 	%Recommendation
\input{chapter7} 	%Conclusion


% APPENDICES
% You have two recommended options for your appendix:
% a) A single appendix (with a single TOC entry)
% b) Multiple appendices. Look under the examples directory for a demo of
%   multiple appendices.
%

\NPSappendices

\chapter{Transfer Functions}
\input{appendix1}

\chapter{Fixed Wing Aircraft Dynamics Model}
\input{appendix2}

\chapter{System Identification}
\input{appendix3}

\chapter{Lyapunov Stability Defintion}
\input{appendix4}

\chapter{Projection Operator}
\input{appendix5}

\chapter{Matlab Code}
\input{appendix6}

%\chapter{Flight Code}
%\input{appendix3}

% REFERENCES
% List all your BibTeX reference source files (ending in *.bib extension)
%
\NPSbibliography{thesis}


%
% This is the official end of the thesis.
%
\NPSend

% DISTRIBUTION LIST
% The list is automatically properly numbered
% and already populated with the mandatory recipients.
%
\NPSdistribution{Initial Distribution List}
\begin{distributionlist}
\item Defense Technical Information Center\\Ft. Belvoir, Virginia
\item Dudley Knox Library\\Naval Postgraduate School\\Monterey, California
%
%---- Other entries are no longer needed, because of Special Abstract Form
% Marine Corps students are required to show:
%\item Marine Corps Representative\\Naval Postgraduate School\\Monterey, California
%\item Directory, Training and Education, MCCDC, Code C46\\Quantico, Virginia
%\item Marine Corps Tactical System Support Activity (Attn: Operations Officer)\\Camp Pendleton, California
%
% Officer students in the Operations Research Program are also required to show:
%\item Director, Studies and Analysis Division, MCCDC, Code C45\\ Quantico, Virginia
%
% Officer students in the Space Ops/Space Engineering Program or in the Information Warfare/Information Systems and Operations are also required to show:
%\item Head, Information Operations and Space Integration Branch,\\ PLI/PP\&O/HQMC, Washington, DC
\end{distributionlist}


\end{document}

